---
title: "비트코인 동향 24"
output: 
  flexdashboard::flex_dashboard:
    theme: cerulean
    css: |
      a {
        color: #000080; /* Dark blue color */
        font-weight: bold; /* Bold font weight */
      }
---

```{r setup, include=FALSE}
#Install thematic and un-comment for themed static plots (i.e., ggplot2)
#thematic::thematic_rmd()
library(DT)
library(flexdashboard)
library(jsonlite)
library(rvest)
library(stringr)
library(dplyr)
library(coronavirus)
library(readr)
library(stringr)
library(knitr)
library(kableExtra)
library(stringr)
library(httr)
library(XML)
library(ggplot2)
library(ggthemes)
library(ggplot2)
library(gganimate)
library(lubridate)
library(transformr)
library(scales)
library(readxl)
library(leaflet)
library(wordcloud)
library(RColorBrewer)

# Install thematic and un-comment for themed static plots (i.e., ggplot2)
# thematic::thematic_rmd()
```

# **국내 비트코인24(업비트)**

## **Column** {.tabset data-width="500"}

### **검색어: 비트코인**

```{r}
# 1. XML로 받기
searchUrl <- "https://openapi.naver.com/v1/search/news.xml"
client_id <- "ZbRRo2N0JNo25YD8n57m"
client_secret <- "nQE2bpCNCa"

search.word <- "비트코인" %>% enc2utf8()
query <- URLencode(search.word)
url <- str_c(searchUrl, "?query=", query, "&display=10")

res <- GET(url,
           add_headers("X-Naver-Client-Id"=client_id,
                       "X-Naver-Client-Secret"=client_secret))
doc <- toString(res)
# 뉴스 Dataframe 생성
xmlFile <- xmlParse(doc)
#xmlRoot(xmlFile)
selected.nodes <- getNodeSet(xmlFile, "//item")

df <- xmlToDataFrame(selected.nodes)

#########################
description <- df[,4]

description2 <- description %>%
    str_remove_all("<b>|</b>|&quot;")

title <- df[,1] %>%
    str_remove_all("<b>|</b>|&quot;")

link <- df[,2]


# 가공된 데이터 적용
description <- df[, 4]
description2 <- description %>% str_remove_all("<b>|</b>|&quot;")
title <- df[, 1] %>% str_remove_all("<b>|</b>|&quot;")
link <- df[, 2]

# 데이터프레임 생성
df_combined <- data.frame(Description = description2,
                          Title = sprintf('<a href="%s">%s</a>', link, title),
                          stringsAsFactors = FALSE)

# 테이블 출력
df_combined <- df_combined %>%
    kable(format="html", escape=FALSE) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
    column_spec(1, width = "35em")

df_combined


```

### **검색어: 코인 상승**

```{r}
# 1. XML로 받기
search.word <- "코인 상승" %>% enc2utf8()
query <- URLencode(search.word)
url <- str_c(searchUrl, "?query=", query, "&display=10")

res <- GET(url,
           add_headers("X-Naver-Client-Id"=client_id,
                       "X-Naver-Client-Secret"=client_secret))
doc <- toString(res)
# 뉴스 Dataframe 생성
xmlFile <- xmlParse(doc)
#xmlRoot(xmlFile)
selected.nodes <- getNodeSet(xmlFile, "//item")

df <- xmlToDataFrame(selected.nodes)

#########################
description <- df[,4]

description2 <- description %>%
    str_remove_all("<b>|</b>|&quot;")

title <- df[,1] %>%
    str_remove_all("<b>|</b>|&quot;")

link <- df[,2]


# 가공된 데이터 적용
description <- df[, 4]
description2 <- description %>% str_remove_all("<b>|</b>|&quot;")
title <- df[, 1] %>% str_remove_all("<b>|</b>|&quot;")
link <- df[, 2]

# 데이터프레임 생성
df_combined <- data.frame(Description = description2,
                          Title = sprintf('<a href="%s">%s</a>', link, title),
                          stringsAsFactors = FALSE)

# 테이블 출력
df_combined <- df_combined %>%
    kable(format="html", escape=FALSE) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
    column_spec(1, width = "35em")

df_combined

```

### **검색어: 코인 하락**

```{r}
# 1. XML로 받기
search.word <- "코인 하락" %>% enc2utf8()
query <- URLencode(search.word)
url <- str_c(searchUrl, "?query=", query, "&display=10")

res <- GET(url,
           add_headers("X-Naver-Client-Id"=client_id,
                       "X-Naver-Client-Secret"=client_secret))
doc <- toString(res)
# 뉴스 Dataframe 생성
xmlFile <- xmlParse(doc)
#xmlRoot(xmlFile)
selected.nodes <- getNodeSet(xmlFile, "//item")

df <- xmlToDataFrame(selected.nodes)

#########################
description <- df[,4]

description2 <- description %>%
    str_remove_all("<b>|</b>|&quot;")

title <- df[,1] %>%
    str_remove_all("<b>|</b>|&quot;")

link <- df[,2]


# 가공된 데이터 적용
description <- df[, 4]
description2 <- description %>% str_remove_all("<b>|</b>|&quot;")
title <- df[, 1] %>% str_remove_all("<b>|</b>|&quot;")
link <- df[, 2]

# 데이터프레임 생성
df_combined <- data.frame(Description = description2,
                          Title = sprintf('<a href="%s">%s</a>', link, title),
                          stringsAsFactors = FALSE)

# 테이블 출력
df_combined <- df_combined %>%
    kable(format="html", escape=FALSE) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
    column_spec(1, width = "35em")

df_combined

```

## **Column** {data-width="350"}

### **비트코인 업비트**

```{r}
res1 <- GET(url = 'https://api.upbit.com/v1/market/all')
coinlist <- res1 %>% content(as = 'text') %>% fromJSON()
coinname <- '비트코인'

# 관심있는 코인의 코드 확인
coin_code <- coinlist[coinlist$korean_name == coinname, 'market']

# 현재 가격 조회
res2 <- GET(url = 'https://api.upbit.com/v1/ticker',
            query = list(markets = "KRW-BTC"))

# 데이터 추출
coinPrice <- res2 %>% content(as = 'text') %>% fromJSON()
prev_closing_price <- coinPrice$prev_closing_price
trade_price <- coinPrice$trade_price
signed_change_price <- coinPrice$signed_change_price
signed_change_rate <- coinPrice$signed_change_rate

# 현재 시세 출력

cat("전일 종가: ", format(prev_closing_price, big.mark = ",", scientific = FALSE), "\n")
cat("현재 시세: ", format(trade_price, big.mark = ",", scientific = FALSE), "\n")

# 변동액에 따른 화살표와 색상 설정
if (signed_change_price > 0) {
  arrow <- "▲"
  color <- "blue"
} else if (signed_change_price < 0) {
  arrow <- "▼"
  color <- "red"
} else {
  arrow <- ""
  color <- "black"
}

# 전일 종가의 변동액 출력
cat("전일 종가의 변동액: ", arrow, format(abs(signed_change_price), big.mark = ",", scientific = FALSE), "\n")

# 전일 종가의 변동율 출력
cat("전일 종가의 변동율: ", arrow, format(signed_change_rate*100, big.mark = ",", scientific = FALSE), "\n")



```

### **비트코인 시간대별 트랜드**

```{r, fig.width=13, fig.height=6}

# 분단위 추출
res3 <- GET(url = 'https://api.upbit.com/v1/candles/minutes/1', query = list(market = 'KRW-BTC', count = 200))
df <- res3 %>% content(as = 'text') %>% fromJSON()

# 시분 추출
df$trade_time <- str_extract(string = df$candle_date_time_kst, pattern = '\\d{2}:\\d{2}')


# 그래프 출력
a <- ggplot(data = df, mapping = aes(x = trade_time, y = trade_price, group = TRUE)) +
      geom_line(color = "blue") +
      theme(axis.text.x = element_text(angle = 95, hjust = 5)) +
      scale_x_discrete(labels = function(x) ifelse(seq_along(x) %% 5 == 0, x, ""))
a+ theme_economist()

```

### **비트코인 월별 트랜드**

```{r, fig.width=13, fig.height=6}
####################################################
#월단위 추출
res4 <- GET(url = 'https://api.upbit.com/v1/candles/months',
            query = list(market = 'KRW-BTC',
            count = 12))
res4 %>% content(as = 'text') %>% fromJSON() -> df


str_extract(string = df$candle_date_time_kst,
            pattern = '(?<=-)\\d{2}-\\d{2}') -> df$trade_days


# Sort the data by trade_days in ascending order
df <- df[order(df$first_day_of_period ), ]

G <- ggplot(data = df, aes(x = first_day_of_period , y = trade_price, group = TRUE)) +
    geom_line() +
    geom_text(aes(label = trade_price), vjust = -1) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 95, hjust = 5))
####################################################
G + theme_economist()


```

# **국외 비트코인24(바이낸스)**

## **Column** {.tabset data-width="500"}

### **검색어: Global Bitcoin adoption**

```{r}
# 1. XML로 받기
searchUrl <- "https://openapi.naver.com/v1/search/news.xml"
client_id <- "ZbRRo2N0JNo25YD8n57m"
client_secret <- "nQE2bpCNCa"

search.word <- "Global Bitcoin adoption" %>% enc2utf8()
query <- URLencode(search.word)
url <- str_c(searchUrl, "?query=", query, "&display=10")

res <- GET(url,
           add_headers("X-Naver-Client-Id"=client_id,
                       "X-Naver-Client-Secret"=client_secret))
doc <- toString(res)
# 뉴스 Dataframe 생성
xmlFile <- xmlParse(doc)
#xmlRoot(xmlFile)
selected.nodes <- getNodeSet(xmlFile, "//item")

df <- xmlToDataFrame(selected.nodes)

#########################
description <- df[,4]

description2 <- description %>%
    str_remove_all("<b>|</b>|&quot;")

title <- df[,1] %>%
    str_remove_all("<b>|</b>|&quot;")

link <- df[,2]


# 가공된 데이터 적용
description <- df[, 4]
description2 <- description %>% str_remove_all("<b>|</b>|&quot;")
title <- df[, 1] %>% str_remove_all("<b>|</b>|&quot;")
link <- df[, 2]

# 데이터프레임 생성
df_combined <- data.frame(Description = description2,
                          Title = sprintf('<a href="%s">%s</a>', link, title),
                          stringsAsFactors = FALSE)

# 테이블 출력
df_combined <- df_combined %>%
    kable(format="html", escape=FALSE) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
    column_spec(1, width = "35em")

df_combined


```

### **검색어: Bitcoin investment trends**

```{r}
# 1. XML로 받기
search.word <- "Bitcoin investment trends" %>% enc2utf8()
query <- URLencode(search.word)
url <- str_c(searchUrl, "?query=", query, "&display=10")

res <- GET(url,
           add_headers("X-Naver-Client-Id"=client_id,
                       "X-Naver-Client-Secret"=client_secret))
doc <- toString(res)
# 뉴스 Dataframe 생성
xmlFile <- xmlParse(doc)
#xmlRoot(xmlFile)
selected.nodes <- getNodeSet(xmlFile, "//item")

df <- xmlToDataFrame(selected.nodes)

#########################
description <- df[,4]

description2 <- description %>%
    str_remove_all("<b>|</b>|&quot;")

title <- df[,1] %>%
    str_remove_all("<b>|</b>|&quot;")

link <- df[,2]


# 가공된 데이터 적용
description <- df[, 4]
description2 <- description %>% str_remove_all("<b>|</b>|&quot;")
title <- df[, 1] %>% str_remove_all("<b>|</b>|&quot;")
link <- df[, 2]

# 데이터프레임 생성
df_combined <- data.frame(Description = description2,
                          Title = sprintf('<a href="%s">%s</a>', link, title),
                          stringsAsFactors = FALSE)

# 테이블 출력
df_combined <- df_combined %>%
    kable(format="html", escape=FALSE) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
    column_spec(1, width = "35em")

df_combined

```

### **검색어: 비트코인 미국**

```{r}
# 1. XML로 받기
search.word <- "비트코인 미국" %>% enc2utf8()
query <- URLencode(search.word)
url <- str_c(searchUrl, "?query=", query, "&display=10")

res <- GET(url,
           add_headers("X-Naver-Client-Id"=client_id,
                       "X-Naver-Client-Secret"=client_secret))
doc <- toString(res)
# 뉴스 Dataframe 생성
xmlFile <- xmlParse(doc)
#xmlRoot(xmlFile)
selected.nodes <- getNodeSet(xmlFile, "//item")

df <- xmlToDataFrame(selected.nodes)

#########################
description <- df[,4]

description2 <- description %>%
    str_remove_all("<b>|</b>|&quot;")

title <- df[,1] %>%
    str_remove_all("<b>|</b>|&quot;")

link <- df[,2]


# 가공된 데이터 적용
description <- df[, 4]
description2 <- description %>% str_remove_all("<b>|</b>|&quot;")
title <- df[, 1] %>% str_remove_all("<b>|</b>|&quot;")
link <- df[, 2]

# 데이터프레임 생성
df_combined <- data.frame(Description = description2,
                          Title = sprintf('<a href="%s">%s</a>', link, title),
                          stringsAsFactors = FALSE)

# 테이블 출력
df_combined <- df_combined %>%
    kable(format="html", escape=FALSE) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
    column_spec(1, width = "35em")

df_combined

```

## **Column** {data-width="350"}

### **비트코인 바이낸스**

```{r}
# API 엔드포인트 URL
url <- "https://api.binance.com/api/v3/ticker/24hr"

# 쿼리 파라미터 설정 (비트코인 시장)
query <- "symbol=BTCUSDT"

# API 호출 및 데이터 가져오기
response <- GET(url, query = query)
data <- content(response, "text") %>%
  jsonlite::fromJSON()

# 현재 시세
current_price <- as.numeric(data$lastPrice)

# 전일 종가
prev_closing_price <- as.numeric(data$prevClosePrice)

# 종가 대비 변동율
price_change_percent <- as.numeric(data$priceChangePercent)

# 종가 대비 변동액
price_change <- as.numeric(data$priceChange)

# 종가 대비 변동율에 따라 화살표 설정
arrow <- ifelse(price_change > 0, "▲", ifelse(price_change < 0, "▼", ""))

# 결과 출력
cat("현재 시세:", current_price, "\n")
cat("전일 종가:", prev_closing_price, "\n")
cat("종가 대비 변동액:", price_change, arrow, "\n")
cat("종가 대비 변동율:", price_change_percent, "%", arrow, "\n")



```

### **비트코인 월별 트랜드**

```{r, fig.width=10, fig.height=10}
####################################################

# API 엔드포인트 URL
url <- "https://api.binance.com/api/v3/klines"

# 쿼리 파라미터 설정 (비트코인 월별 데이터)
symbol <- "BTCUSDT"
interval <- "1M"
limit <- 1000

# API 호출 및 데이터 가져오기
response <- GET(url, query = list(symbol = symbol, interval = interval, limit = limit))
data <- content(response, "text") %>% fromJSON()

# 데이터 프레임 변환
df <- as.data.frame(data)

# 컬럼명 설정
colnames(df) <- c("Open Time", "Open", "High", "Low", "Close", "Volume", "Close Time", "Quote Asset Volume", "Number of Trades", "Taker Buy Base Asset Volume", "Taker Buy Quote Asset Volume", "Ignore")

# 시간 형식 변환
df$`Open Time` <- as.POSIXct(as.numeric(df$`Open Time`) / 1000, origin = "1970-01-01")

# 월별 데이터로 변환
df$Month <- format(df$`Open Time`, "%Y-%m")

# 월별 시세 계산
monthly_prices <- df %>%
    group_by(Month) %>%
    summarise(Open = first(Open), High = max(High), Low = min(Low), Close = last(Close))


# Print the selected data
selected_data <- monthly_prices %>%
    select(Month, Close)


recent_data <- selected_data %>%
    filter(Month >= format(Sys.Date()-730, "%Y-%m"))


#recent_data$Month <- ymd(recent_data$Month)  # Convert Month column to Date format



 # Your code to generate the plot
 # ...
 

G_plotly <- ggplot(recent_data, aes(x = Month, y = as.numeric(Close))) +
    geom_bar(stat = "identity", fill = "blue", width = 0.5) +
    geom_text(aes(label = Close), vjust = -0.5, color = "white") +
    labs(title = "Monthly Prices", x = "Month", y = "Price") +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        panel.background = element_rect(fill = "black"),
        plot.background = element_rect(fill = "black"),
        plot.title = element_text(color = "yellow", size = 30),
        axis.title = element_text(color = "white", size = 20),
        axis.text = element_text(color = "white", size = 15),
        panel.grid = element_line(color = "white"),
        panel.grid.major.x = element_blank()
    )

G_plotly


```

# **미귝 채권&유가&M1(일별 트랜드)**

### **미국 채권 일자별 트랜드**

```{r}
library(plotly)

# Read the data
spread_data <- read.csv("미국 10년채 2년채 스프레드_일별.csv")
yield2_data <- read.csv("2년채_수익율_일별.csv")
yield10_data <- read.csv("10년채_수익율_일별.csv")

# Convert DATE column to date format
spread_data$DATE <- as.Date(spread_data$DATE)
yield2_data$DATE <- as.Date(yield2_data$DATE)
yield10_data$DATE <- as.Date(yield10_data$DATE)

# Subset data for the most recent 2 years
recent_spread_data <- subset(spread_data, DATE >= max(DATE) - 365*2)
recent_yield2_data <- subset(yield2_data, DATE >= max(DATE) - 365*2)
recent_yield10_data <- subset(yield10_data, DATE >= max(DATE) - 365*2)

# Create the bond visualization
bond_graph <- plot_ly() %>%
    add_trace(
        data = recent_spread_data,
        x = ~DATE,
        y = ~T10Y2Y,
        type = "scatter",
        mode = "lines",
        name = "Spread",
        line = list(color = "blue")
    ) %>%
    add_trace(
        data = recent_yield2_data,
        x = ~DATE,
        y = ~DGS2,
        type = "scatter",
        mode = "lines",
        name = "2-Year Yield",
        line = list(color = "red")
    ) %>%
    add_trace(
        data = recent_yield10_data,
        x = ~DATE,
        y = ~DGS10,
        type = "scatter",
        mode = "lines",
        name = "10-Year Yield",
        line = list(color = "green")
    ) %>%
    layout(
        xaxis = list(title = "Date", tickformat = "%Y-%m", dtick = "M1"),
        yaxis = list(title = "Value"),
        showlegend = TRUE,
        plot_bgcolor = "#ffffff",
        paper_bgcolor = "#ffffff",
        font = list(color = "#333333")
    )

# Apply the theme
theme <- list(
    layout = list(
        xaxis = list(title = list(font = list(size = 14))),
        yaxis = list(title = list(font = list(size = 14))),
        legend = list(font = list(size = 12))
    )
)

# Apply the theme to the plot
bond_graph <- bond_graph %>% config(displayModeBar = FALSE) %>% layout(theme)

# Display the bond visualization
bond_graph

```

### **국제 유가 & M1 일자별 트랜드**

```{r}

library(plotly)

# 데이터 읽기
oil_data <- read.csv("국제 유가_일별.csv")
m1_data <- read.csv("M1_일별.csv")

# Convert DATE column to date format
oil_data$DATE <- as.Date(oil_data$DATE)
m1_data$DATE <- as.Date(m1_data$DATE)

# 최근 12개월 데이터 선택
recent_oil_data <- subset(oil_data, DATE >= max(DATE) - 365*2)
recent_m1_data <- subset(m1_data, DATE >= max(DATE) - 365*2)

# 그래프 생성 - Oil Price
graph_oil <- plot_ly(recent_oil_data, x = ~DATE, y = ~DCOILWTICO, type = "scatter", mode = "lines", name = "Oil Price")

# 레이아웃 설정 - Oil Price
layout_oil <- list(
    title = "International Oil Price",
    xaxis = list(title = "Date"),
    yaxis = list(title = "Oil Price")
)

# 그래프 생성 - M1 Money Supply
graph_m1 <- plot_ly(recent_m1_data, x = ~DATE, y = ~WM1NS, type = "scatter", mode = "lines", name = "M1 Money Supply")

# 레이아웃 설정 - M1 Money Supply
layout_m1 <- list(
    title = "M1 Money Supply",
    xaxis = list(title = "Date"),
    yaxis = list(title = "M1")
)

# 그래프 출력
fig_oil <- graph_oil %>% layout(layout_oil)
fig_m1 <- graph_m1 %>% layout(layout_m1)

# 그래프를 서브플롯으로 나란히 출력
subplot(fig_oil, fig_m1, nrows = 2)



```

### **검색어: 미국 채권 유가 M1**

```{r}
# 1. XML로 받기
searchUrl <- "https://openapi.naver.com/v1/search/news.xml"
client_id <- "ZbRRo2N0JNo25YD8n57m"
client_secret <- "nQE2bpCNCa"

search.word <- "미국 채권 유가 M1" %>% enc2utf8()
query <- URLencode(search.word)
url <- str_c(searchUrl, "?query=", query, "&display=10")

res <- GET(url,
           add_headers("X-Naver-Client-Id"=client_id,
                       "X-Naver-Client-Secret"=client_secret))
doc <- toString(res)
# 뉴스 Dataframe 생성
xmlFile <- xmlParse(doc)
#xmlRoot(xmlFile)
selected.nodes <- getNodeSet(xmlFile, "//item")

df <- xmlToDataFrame(selected.nodes)

#########################
description <- df[,4]

description2 <- description %>%
    str_remove_all("<b>|</b>|&quot;")

title <- df[,1] %>%
    str_remove_all("<b>|</b>|&quot;")

link <- df[,2]


# 가공된 데이터 적용
description <- df[, 4]
description2 <- description %>% str_remove_all("<b>|</b>|&quot;")
title <- df[, 1] %>% str_remove_all("<b>|</b>|&quot;")
link <- df[, 2]
# 데이터프레임 생성
df_combined <- data.frame(
  Title = sprintf('<a href="%s">%s</a>', link, title),
  Description = description2,
  stringsAsFactors = FALSE
)

# Reorder the columns
df_combined <- df_combined[, c("Title", "Description")]

# 테이블 출력
df_combined <- df_combined %>%
  kable(format = "html", escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(1, width = "35em")

df_combined

 
```

# **미국 월별 경제지표**

### **미국 CPI, 실업율, 금수출 월별 트랜드** {data-width="650"}

```{r}
URL <- "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=718&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=CPIAUCSL&scale=left&cosd=1947-01-01&coed=2023-03-01&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=avg&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=lin&vintage_date=2023-05-07&revision_date=2023-05-07&nd=1947-01-01"
data <- read_csv(URL)

# DATE 컬럼을 날짜 형식으로 변환
data$DATE <- as.Date(data$DATE)

# 조건에 맞는 데이터 추출
filtered_data <- data[data$DATE >= as.Date("2009-01-01"), ]

write.csv(filtered_data, file = "cpi_월별.csv", row.names = FALSE)


# 미국 실업률 데이터 2009 ~ 최신
URL <- "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=718&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=UNRATE&scale=left&cosd=1948-01-01&coed=2023-04-01&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=avg&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=lin&vintage_date=2023-05-07&revision_date=2023-05-07&nd=1948-01-01"
data <- read_csv(URL)

# DATE 컬럼을 날짜 형식으로 변환
data$DATE <- as.Date(data$DATE)

# 조건에 맞는 데이터 추출
filtered_data <- data[data$DATE >= as.Date("2009-01-01"), ]


write.csv(filtered_data, file = "실업률_월별.csv", row.names = FALSE)

# 금수출 데이터 2009 ~ 최신
URL <- "https://fred.stlouisfed.org/graph/fredgraph.csv?bgcolor=%23e1e9f0&chart_type=line&drp=0&fo=open%20sans&graph_bgcolor=%23ffffff&height=450&mode=fred&recession_bars=on&txtcolor=%23444444&ts=12&tts=12&width=718&nt=0&thu=0&trc=0&show_legend=yes&show_axis_titles=yes&show_tooltip=yes&id=IQ12260&scale=left&cosd=1984-12-01&coed=2023-03-01&line_color=%234572a7&link_values=false&line_style=solid&mark_type=none&mw=3&lw=2&ost=-99999&oet=99999&mma=0&fml=a&fq=Monthly&fam=avg&fgst=lin&fgsnd=2020-02-01&line_index=1&transformation=lin&vintage_date=2023-05-07&revision_date=2023-05-07&nd=1984-12-01"
data <- read_csv(URL)

# DATE 컬럼을 날짜 형식으로 변환
data$DATE <- as.Date(data$DATE)

# 조건에 맞는 데이터 추출
filtered_data <- data[data$DATE >= as.Date("2009-01-01"), ]


write.csv(filtered_data, file = "금수출_월별.csv", row.names = FALSE)


# Read the CPI data
cpi_data <- read.csv("cpi_월별.csv")
# Read the unemployment rate data
unemployment_data <- read.csv("실업률_월별.csv")
# Read the gold exports data
gold_exports_data <- read.csv("금수출_월별.csv")

# Convert DATE column to date format
cpi_data$DATE <- as.Date(cpi_data$DATE)
unemployment_data$DATE <- as.Date(unemployment_data$DATE)
gold_exports_data$DATE <- as.Date(gold_exports_data$DATE)

# Create CPI plotly graph with title
cpi_plot <- plot_ly(data = cpi_data, x = ~DATE, y = ~CPIAUCSL, type = "scatter", mode = "lines", line = list(color = "blue", width = 1.4)) %>%
  layout(title = list(text = "Consumer Price Index (CPI)", x = 1.5),
         xaxis = list(title = "Date"),
         yaxis = list(title = "CPI"),
         showlegend = FALSE)

# Create unemployment rate plotly graph with title
unemployment_plot <- plot_ly(data = unemployment_data, x = ~DATE, y = ~UNRATE, type = "scatter", mode = "lines", line = list(color = "red", width = 1.4)) %>%
  layout(title = list(text = "Unemployment Rate", x = 1.5),
         xaxis = list(title = "Date"),
         yaxis = list(title = "Unemployment Rate"),
         showlegend = FALSE)

# Create gold exports plotly graph with title
gold_exports_plot <- plot_ly(data = gold_exports_data, x = ~DATE, y = ~IQ12260, type = "scatter", mode = "lines", line = list(color = "darkgreen", width = 1.4)) %>%
  layout(title = list(text = "미국 CPI  &  Unemployment Rate  &  Gold Exports", x = 1.5, font = list(size = 35)),
         xaxis = list(title = "Date"),
         yaxis = list(title = "미국 CPI,  &  Unemployment Rate  &  Gold Exports"),
         showlegend = FALSE)

# Combine the graphs vertically
combined_plot <- subplot(cpi_plot, unemployment_plot, gold_exports_plot, nrows = 1)

combined_plot <- layout(combined_plot)

combined_plot <- layout(combined_plot, margin = list(l = 90, r = 90, t = 90, b = 90))

# Display the combined plot
combined_plot
```

### **검색어: 미국 CPI, 실업율, 금수출** {data-width="650"}

```{r}
# 1. XML로 받기
searchUrl <- "https://openapi.naver.com/v1/search/news.xml"
client_id <- "ZbRRo2N0JNo25YD8n57m"
client_secret <- "nQE2bpCNCa"

search.word <- "미국 CPI" %>% enc2utf8()
query <- URLencode(search.word)
url <- str_c(searchUrl, "?query=", query, "&display=10")

res <- GET(url,
           add_headers("X-Naver-Client-Id"=client_id,
                       "X-Naver-Client-Secret"=client_secret))
doc <- toString(res)
# 뉴스 Dataframe 생성
xmlFile <- xmlParse(doc)
#xmlRoot(xmlFile)
selected.nodes <- getNodeSet(xmlFile, "//item")

df <- xmlToDataFrame(selected.nodes)

#########################
description <- df[,4]

description2 <- description %>%
    str_remove_all("<b>|</b>|&quot;")

title <- df[,1] %>%
    str_remove_all("<b>|</b>|&quot;")

link <- df[,2]


# 가공된 데이터 적용
description <- df[, 4]
description2 <- description %>% str_remove_all("<b>|</b>|&quot;")
title <- df[, 1] %>% str_remove_all("<b>|</b>|&quot;")
link <- df[, 2]

# 데이터프레임 생성
df_combined <- data.frame(
  Title = sprintf('<a href="%s">%s</a>', link, title),
  Description = description2,
  stringsAsFactors = FALSE
)

# Reorder the columns
df_combined <- df_combined[, c("Title", "Description")]

# 테이블 출력
df_combined <- df_combined %>%
  kable(format = "html", escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(1, width = "35em")

df_combined


```

# **한국 경제지표**

## **Row**

### **한국은행 기준 국내 명목 GDP**

```{r}

d <- Sys.Date() - 1
date <- format(d, "%Y%m%d")
month <- format(d, "%Y%m")
year <- format(d, "%Y")

end_date <- paste0(month, "/")
#한국은행

###################  gdp
api_key <- "1ODEWEJ6C0GR31YD2FXD/"
url <- paste0("https://ecos.bok.or.kr/api/StatisticSearch/1ODEWEJ6C0GR31YD2FXD/JSON/kr/1/100000/200Y001/A/2009/",year ,"/10101/?/?/?")
raw.data <- readLines(url, warn = "F", encoding = "UTF-8")
dat <- fromJSON(raw.data)

# Extract relevant data
time <- dat$StatisticSearch$row$TIME
data_value <- dat$StatisticSearch$row$DATA_VALUE

# Create dataframe
df <- data.frame(Time = time, Data_Value = data_value)
#, decreasing = TRUE
df <- df[order(df$Time), ]

df$Data_Value <- as.numeric(df$Data_Value)
df$Difference <- c(NA, diff(df$Data_Value))



# Create the bar plot
bar_plot <- ggplot(df) +
    aes(x = Time, y = Data_Value) +
    geom_col(fill = "#112446") +
    labs(x = "Time", y = "Data Value", title = "한국 GDP") +
    theme_minimal() +
    theme(
        plot.title = element_text(size = 16, face = "bold"),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"),
        panel.border = element_blank()
    )

# Create the line plot with the secondary axis
line_plot <- ggplot(df) +
    aes(x = Time, y = Difference) +
    geom_line(color = "#FF5733", size = 1, group = 1) +
    geom_point(color = "#FF5733", size = 3) +
    labs(y = "Difference", title = "Difference from Previous Value") +
    theme_minimal() +
    theme(
        plot.title = element_text(size = 16, face = "bold"),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"),
        panel.border = element_blank()
    ) +
    scale_y_continuous(
        sec.axis = sec_axis(
            ~.,
            name = "Difference",
            breaks = pretty(df$Difference),
            labels = scales::comma
        )
    )


plot_combined <- cowplot::plot_grid(bar_plot, line_plot, align = "v", ncol = 1)

# Display the combined plot with larger size
plot_combined
```

------------------------------------------------------------------------

### **한국 금리**

```{r}

###################  금리
api_key <- "1ODEWEJ6C0GR31YD2FXD/"
url <- paste0("https://ecos.bok.or.kr/api/StatisticSearch/1ODEWEJ6C0GR31YD2FXD/JSON/kr/1/10000/722Y001/M/200901/",month ,"/0101000/?/?/?")
raw.data <- readLines(url, warn = "F", encoding = "UTF-8")
dat <- fromJSON(raw.data)

# Extract relevant data
time <- dat$StatisticSearch$row$TIME
data_value <- dat$StatisticSearch$row$DATA_VALUE

# Create dataframe
df <- data.frame(Time = time, Data_Value = data_value)


df$Time <- as.Date(paste0(substr(df$Time, 1, 4), "-", substr(df$Time, 5, 6), "-01"))

a<- ggplot(df, aes(x = Time, y = Data_Value)) +
    geom_point(color = "#112446", size = 1.5) +
    labs(x = "", y = "") +
    theme_minimal() +
    theme(
        plot.title = element_text(size = 16, face = "bold"),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"),
        panel.border = element_blank()
    )

# Convert ggplot to plotly
plotly_obj <- ggplotly(a)

# Show the plotly object

datatable_df <- DT::datatable(df, options = list(pageLength = 5))
datatable_df 
```

### **한국 금리 그래프**

```{r}
plotly_obj 
```

## **Row**

### **검색어: 한국 경제 금리**

```{r}
# 1. XML로 받기
searchUrl <- "https://openapi.naver.com/v1/search/news.xml"
client_id <- "ZbRRo2N0JNo25YD8n57m"
client_secret <- "nQE2bpCNCa"

search.word <- "한국 경제 금리" %>% enc2utf8()
query <- URLencode(search.word)
url <- str_c(searchUrl, "?query=", query, "&display=30")

res <- GET(url,
           add_headers("X-Naver-Client-Id"=client_id,
                       "X-Naver-Client-Secret"=client_secret))
doc <- toString(res)
# 뉴스 Dataframe 생성
xmlFile <- xmlParse(doc)
#xmlRoot(xmlFile)
selected.nodes <- getNodeSet(xmlFile, "//item")

df <- xmlToDataFrame(selected.nodes)

#########################
description <- df[,4]

description2 <- description %>%
    str_remove_all("<b>|</b>|&quot;")

title <- df[,1] %>%
    str_remove_all("<b>|</b>|&quot;")

link <- df[,2]


# 가공된 데이터 적용
description <- df[, 4]
description2 <- description %>% str_remove_all("<b>|</b>|&quot;")
title <- df[, 1] %>% str_remove_all("<b>|</b>|&quot;")
link <- df[, 2]
# 데이터프레임 생성
df_combined <- data.frame(
  Title = sprintf('<a href="%s">%s</a>', link, title),
  stringsAsFactors = FALSE
)

# Reorder the columns
df_combined <- df_combined[, "Title", drop = FALSE]

# 테이블 출력
df_combined <- df_combined %>%
  kable(format = "html", escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(1, width = "35em")

df_combined



```

## **Column** {.tabset}

### **CPI**

```{r}

d <- Sys.Date() - 1
date <- format(d, "%Y%m%d")
month <- format(d, "%Y%m")
year <- format(d, "%Y")

api_key <- "1ODEWEJ6C0GR31YD2FXD/"
file_type <- "json/"
lang_type <- "kr/"
start_no <- "1/"
end_no <- "1000/"
stat_code <- "901Y009/" # 소비자 물가지수 (A,M,Q)
cycle_type <- "M/"
start_date <- "200901/"
end_date <- paste0(month, "/")
item_no <- "0"

url <- paste0("https://ecos.bok.or.kr/api/StatisticSearch/",
              api_key, file_type, lang_type, start_no, end_no,
              stat_code, cycle_type, start_date, end_date, item_no)
raw.data <- readLines(url, warn = "F", encoding = "UTF-8")
dat <- fromJSON(raw.data)

# Extract relevant data
time <- dat$StatisticSearch$row$TIME
data_value <- dat$StatisticSearch$row$DATA_VALUE


# Create dataframe
df <- data.frame(Time = time, Data_Value = data_value)

df$Data_Value <- as.numeric(as.character(df$Data_Value))
df$Data_Value <- round(df$Data_Value, 2)

# Extract year and month from Time column
df$Year <- substr(df$Time, 1, 4)
df$Month <- substr(df$Time, 5, 6)

# Convert Year and Month columns to date format
df$Date <- ymd(paste(df$Year, df$Month, "01"))

# Create a line plot with animated months
p <- ggplot(df, aes(x = Date, y = Data_Value, group = 1)) +
    geom_line(color = "#3366cc", size = 3.5) +
    labs(title = "소비자 물가지수", x = "Date", y = "Data Value") +
    theme_minimal() +
    theme(plot.title = element_text(size = 26, face = "bold"),
          axis.title.x = element_text(size = 22),
          axis.title.y = element_text(size = 22),
          axis.text.x = element_text(size = 20),
          axis.text.y = element_text(size = 20),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.border = element_blank(),
          legend.position = "none")



rd_anim <- p +
  transition_reveal(Date) +
  labs(
    subtitle = "Date: {frame_along}"
  ) +
  theme(plot.subtitle = element_text(size = 36))

animate(rd_anim,
        height = 980,
        width = 700,
        duration = 5, 
        end_pause = 15)



```

### **CPI Summary**

```{r}


# Filter data for the past year
past_year <- df %>%
    mutate(Month = paste(Year, Month, sep = "-")) %>%
    filter(Date >= (Sys.Date() - years(15)))

# Group filtered data by month and calculate summary statistics
monthly_summary <- past_year %>%
    group_by(Year) %>%
    summarise(
        Mean = round(mean(Data_Value), 2),
        Min = round(min(Data_Value), 2),
        Max = round(max(Data_Value), 2)
    )
library(kableExtra)
# Print the formatted monthly summary table
kable(monthly_summary, align = c("l", "c", "c", "c"), caption = "Yearly Summary") %>%
    kable_styling(bootstrap_options = "striped", full_width = FALSE)

```
